Adopting agile software development in the large organizations: A systematic literature review

### 2014-08-10 journal/content.tex
Missing comma

Typical challenges included change resistance and lack of commitment and
investment in transformation. Some challenges related particularly to large
scale, such as implementing effective coordination between teams, and friction
caused by the fact that a large organization can not transform all at once.
The most important success factors were management support, use of training and
coaching and carefully customizing the agile model to fit the organization.

>>>>

Typical challenges included change resistance and lack of commitment and
investment in transformation. Some challenges related particularly to large
scale, such as implementing effective coordination between teams, and friction
caused by the fact that a large organization can not transform all at once.
The most important success factors were management support, use of training and
coaching, and carefully customizing the agile model to fit the organization.
